Manuscript

### 2022-09-09 analysis/manuscript.Rmd
change name to summ C from max C

max_C_plot <- ggplot2::ggplot(data = summ_C_data, 
                              ggplot2::aes(x = corr_due_to_confounding_summ, 
                                           y = same_trait_corr_minus_MR_est, 
                                           label = Phenotype)) +

@@

  theme_minimal() +
  ggplot2::labs(x = paste0("C-sum"),
                y = paste("Correlation - MR-estimate")) +
  theme(legend.title=element_blank()) +
  geom_text_repel(data = subset(max_C_data, label_phenos==TRUE),
                  nudge_y = -0.25 - subset(max_C_data, label_phenos==TRUE)$same_trait_corr_minus_MR_est, size = 3.25,
                  direction = "x", show.legend = FALSE, box.padding = 0.5)

max_C_plot

>>>>

summ_C_plot <- ggplot2::ggplot(data = summ_C_data, 
                              ggplot2::aes(x = corr_due_to_confounding_summ, 
                                           y = same_trait_corr_minus_MR_est, 
                                           label = Phenotype)) +

@@

  theme_minimal() +
  ggplot2::labs(x = paste0("C-sum"),
                y = paste("Correlation - MR-estimate")) +
  theme(legend.title=element_blank()) +
  geom_text_repel(data = subset(summ_C_data, label_phenos==TRUE),
                  nudge_y = -0.25 - subset(summ_C_data, label_phenos==TRUE)$same_trait_corr_minus_MR_est, size = 3.25,
                  direction = "x", show.legend = FALSE, box.padding = 0.5)

summ_C_plot
